Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-05-07 Scripts/Initial_Analysis.Rmd
fixed point in fig4

  # Identify SSR treshold for natural spatial variability of the stock
  proportion_tresh <- proportion_data %>% 
    filter(time_step == "historical") %>% 
    mutate(
      top_tresh = ensemble_mean+(2*ensemble_sd), # two s.d.
      low_tresh = ensemble_mean-(2*ensemble_sd) # two.s.d
    ) %>% 
    select(taxon_key:eez_neighbour,top_tresh:low_tresh) %>% 
    left_join(proportion_data) %>% 
    # Only keeps change if surpasses treshold
    mutate(
      over_tresh = ifelse(ensemble_mean > top_tresh | ensemble_mean < low_tresh,"keep",
                          ifelse(time_step == "historical","keep","drop")
      )
    ) %>% 
    filter(over_tresh == "keep") %>% 
    select(-top_tresh,-low_tresh)

@@

@@

  proportion_change <- eez %>% 
    gather("variable","value",n_spp:n_per) %>% 
    spread(time_step,value) %>% 
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    # funs(round(((.-historical)/(abs(historical)))*100,2)
    funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2)
                )
         )
    )

@@

  Prop_map <- ggplot() +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
    geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
               aes(start_lon,
                   start_lat
               ),
               size = 0.05,
               col = "gray80",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(paths, time_step == time & per_plot > 0),
              aes(X,
                  Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 0.3,
              lineend = "round",
              arrow = arrow(length = unit(0.008, "npc"),
                            ends = "first"),
              show.legend = NA) +
    # Closeup Rectangles 
    # geom_rect(data=Rectangles,
    #           aes(xmin=x1, 
    #               xmax=x2,
    #               ymin=y1,
    #               ymax=y2),
    #           color="grey50", 
    #           fill = NA,
    #           linetype = "dashed"
    # ) +
    my_ggtheme_m() +
    scale_colour_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # option="magma",
      # direction = -1
    ) +
    scale_fill_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # alpha = 0.8
      # option="magma",
      # direction = -1
    ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )

>>>>

  # Identify SSR treshold for natural spatial variability of the stock
  proportion_tresh <- proportion_data %>% 
    filter(time_step == "historical") %>% 
    mutate(
      top_tresh = ensemble_mean+(2*ensemble_sd), # two s.d.
      low_tresh = ensemble_mean-(2*ensemble_sd) # two.s.d
    ) %>% 
    select(taxon_key:eez_neighbour,top_tresh:low_tresh) %>% 
    left_join(proportion_data) %>% 
    # Only keeps change if surpasses treshold
    mutate(
      over_tresh = ifelse(time_step != "historical" & ensemble_mean > top_tresh | ensemble_mean < low_tresh,"keep",
                          ifelse(time_step == "historical","keep","drop")
      )
    ) %>% 
    # filter(time_step !="historical" | over_tresh == "keep") %>%
    filter(over_tresh == "keep") %>%
    select(-top_tresh,-low_tresh)

@@

#### Fun `EEZarrive_exit`

```{r fun_EEZexit, eval = F, echo = F}

# taxon_list <- c(600004,600006)

# EEZProp <- function(taxon_list,links="NA"){

  spp <- bind_rows(
    lapply(Taxon_list,SummaryProp,links)
  ) %>% 
    spread(time_step,mean_spp) %>% 
    # mutate_if(is.numeric,replace_na,0) %>% # If NA 0 meaning wins and looses
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    funs(round(((.-historical)/(abs(historical)))*100,2))) %>%  # original
         # funs(round(((historical-.)/(abs((historical+.)/2)))*100,2)
    # funs((historical-.)*100)) %>%  
    # funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2)
                # )
         # )
    # ) %>%
  gather("time_step","percentage_change",per_early:per_mid)

@@

  proportion_change <- eez %>% 
    gather("variable","value",n_spp:n_per) %>% 
    spread(time_step,value) %>% 
    mutate_at(vars(
      "per_early" = early,
      "per_mid" = mid
    ),
    # funs(round(((.-historical)/(abs(historical)))*100,2)
    funs(ifelse(variable == "n_per",.,round(((.-historical)/(abs(historical)))*100,2) # original
    #             )
    # funs(ifelse(variable == "n_per",.,(historical-.)*100)
                )
         )
    )

@@

  Prop_map <- ggplot() +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
    geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_point(data = subset(Map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
               aes(start_lon,
                   start_lat
               ),
               size = 0.05,
               col = "gray80",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
              aes(X,
                  Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 0.3,
              lineend = "round",
              arrow = arrow(length = unit(0.008, "npc"),
                            ends = "first"),
              show.legend = NA) +
    # Closeup Rectangles 
    # geom_rect(data=Rectangles,
    #           aes(xmin=x1, 
    #               xmax=x2,
    #               ymin=y1,
    #               ymax=y2),
    #           color="grey50", 
    #           fill = NA,
    #           linetype = "dashed"
    # ) +
    my_ggtheme_m() +
    scale_colour_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # option="magma",
      # direction = -1
    ) +
    scale_fill_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # alpha = 0.8
      # option="magma",
      # direction = -1
    ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )
